A tutorial on how to do the same thing more than once

### 2021-08-06 manuscript.Rmd
closes #188

1.	**Multiple inconsistent versions of code, data, or both**; for example, the data set could have changed over time because outliers were removed at a later stage or an item was later recoded; or, the analysis code could have been modified during writing of a paper because a bug was removed at some point in time
It may then be unclear which version of code and data was used to produce some reported set of results.
2.	**Copy-and-paste errors**; for example, results are often manually copied from a statistical computing language into a text processor; if a given analysis is re-run and results are manually updated in the text processor, this may inadvertently lead to inconsistencies between the reported result and the reproduced result;
3.	**Undocumented or ambiguous order of code execution**; for example, with multiple data and code files, it may be unclear which scripts should be executed in what order;  or, some of the computational steps are documented (e.g., final analysis), but other steps were conducted manually without documentation (e.g., executing a command manually instead of in a script; copy-pasting results from one program to another)
4.	**Ambiguous dependencies**; for example, a given analysis may depend on a specific version of a specific software package, or rely on software that might not be available on a different computer or no longer exist at all; or, a different version of the same software may produce different results.

>>>>

1.	**Multiple inconsistent versions of code, data, or both**; for example, the data set could have changed over time because outliers were removed at a later stage or an item was later recoded; or, the analysis code could have been modified during writing of a paper because a bug was removed at some point in time
It may then be unclear which version of code and data was used to produce some reported set of results.
2.	**Copy-and-paste errors**; for example, results are often manually copied from a statistical computing language into a text processor; if a given analysis is re-run and results are manually updated in the text processor, this may inadvertently lead to inconsistencies between the reported result and the reproduced result;
3.	**Undocumented or ambiguous order of computation**; for example, with multiple data and code files, it may be unclear which scripts should be executed in what order;  or, some of the computational steps are documented (e.g., final analysis), but other steps were conducted manually without documentation (e.g., executing a command manually instead of in a script; copy-pasting results from one program to another)
4.	**Ambiguous dependencies**; for example, a given analysis may depend on a specific version of a specific software package, or rely on software that might not be available on a different computer or no longer exist at all; or, a different version of the same software may produce different results.
